Local Search Algorithms for the Maximum Carpool Matching Problem

### 2017-10-29 src/appendix.tex
merge dror
refactor figs ins
foo
sub figure

%\newpage
%\bigskip

@@

\begin{figure}[h]
\centering
\input{fig-submodular}
\caption[]{%
Given the two solutions on the left, 
\subref{sub:cup} and \subref{sub:cap}, we
can construct the two solutions on the right side,
\subref{sub:s} and \subref{sub:t}, with equal total weight.
The edges of type 
\inlineedge{e1}, 
\inlineedge{e2}, 
\inlineedge{e3}, 
\inlineedge{e5}, 
\inlineedge{e6}
from the left side are ``naturally'' distributed over the two solutions on the
right side and the edges of type \inlineedge{e4} can be distributed between the
two solutions without violating the capacity constraints.
}
\label{fig:sub}
\end{figure}

@@

\medskip

@@

\begin{figure}[h]
\begin{center}
\scalebox{.85}{\input{fig-local-tight}}
\caption{A tight example for Corollary~\ref{cor:local}. 
The optimal solution is given by the red solid arcs while the local
search solution is given by the green, dashed arcs.  The solution can
be improved by the local search algorithm only if it removes all the
edges.}
\label{fig:local search tight}
\end{center}
\end{figure}

>>>>

\newpage

@@

@@

\newpage

@@

\begin{figure}[h]
\begin{center}
\scalebox{.9}{
\input{fig-local-tight}
}
\caption{A tight example for Corollary~\ref{cor:local}. 
The optimal solution is given by the red solid arcs while the local
search solution is given by the green, dashed arcs.  The solution can
be improved by the local search algorithm only if it removes all the
edges.}
\label{fig:local search tight}
\end{center}
\end{figure}

### 2017-10-29 src/sub.tex
sub figure

>>>>

\begin{figure}[h]
\centering
\input{fig-submodular}
\caption[]{%
Given the two solutions on the left, 
\subref{sub:cup} and \subref{sub:cap}, we
can construct the two solutions on the right side,
\subref{sub:s} and \subref{sub:t}, with equal total weight.
The edges of type 
\inlineedge{e1}, 
\inlineedge{e2}, 
\inlineedge{e3}, 
\inlineedge{e6}
from the left side are ``naturally'' distributed over the two solutions on the
right side and the edges of type \inlineedge{e5} and \inlineedge{e4} can be
distributed between the two solutions without violating the capacity constraints.
}
\label{fig:sub}
\end{figure}
